Two Decades of Smalltalk VM Development

### 2018-08-17 paper.tex
typo

In this section we first discuss the VM simulator limits and how we work around them, then the interaction between the simulator and bootstrapping processes. Lastly, we mention some relevant related works.

>>>>

In this section we first discuss the VM simulator limitations and how we work around them, then the interaction between the simulator and bootstrapping processes. Lastly, we mention some relevant related works.
